Rapid-response Bayesian sky localization for electromagnetic follow-up of gravitational-wave candidates

### 2013-03-07 ms.tex
Probably not the correct number of parameters
Fix spelling error

A \ac{CBC} source is described by a 15\nobreakdashes-dimensional parameter vector,
\begin{equation}
    \boldsymbol\theta = \begin{array}{l@{}l}
            \left[
            \begin{array}{c}
                \alpha \\
                \delta \\
                t_\oplus \\
                \iota \\
                \psi \\
                \phi_c \\
                \hdashline[1pt/1pt]
                m_1 \\
                m_2 \\
                \mathbf S_1 \\
                \mathbf S_2
            \end{array}
            \right] &
            \begin{array}{l}
                \left.
                \begin{array}{p{4cm}}
                    right ascension \\
                    declination \\
                    arrival time at geocenter \\
                    inclination angle \\
                    polarization angle \\
                    coalescence phase \\
                    \hdashline[1pt/1pt]
                \end{array}
                \quad \right\} \textnormal{extrinsic} \\
                \left.
                \begin{array}{p{4cm}}
                    first component's mass \\
                    second component's mass \\
                    first component's spin \\
                    second component's spin
                \end{array}
                \quad \right\} \textnormal{intrinsic}
            \end{array}
        \end{array}
\end{equation}

In this work we restrict ourselves to non-spinng sources, where $\mathbf{S}_1=\mathbf{S}_2=0$. Removing nuisance parameters requires either replacing them with their measured values or marginalizing over them. The chirp mass is typically well measured by the detection pipeline, so we use the maximum likelihood value, $\hat{\mathcal{M}}$, for it. We marginalize over the other variables using a uniform prior, i.e.
\begin{equation}
p(\alpha,\delta,D_L|d) = \int\, d\tau_\oplus p_U(\tau_\oplus) d\phi_c p_U(\phi_c) d\phi p_U(\psi)  d\cos(\iota) p_U(\cos(\iota)) p(\alpha,\delta,D_L,\tau_\oplus,\phi_c,\psi,\cos(\iota)|d),
\end{equation}
where $p_U(x)$ denotes a uniform distribution in $x$.

>>>>

A \ac{CBC} source is described by a 15\nobreakdashes-dimensional%
%
\marginpar{Check the number of parameters.}
%
parameter vector,
\begin{equation}
    \boldsymbol\theta = \begin{array}{l@{}l}
            \left[
            \begin{array}{c}
                \alpha \\
                \delta \\
                t_\oplus \\
                \iota \\
                \psi \\
                \phi_c \\
                \hdashline[1pt/1pt]
                m_1 \\
                m_2 \\
                \mathbf S_1 \\
                \mathbf S_2
            \end{array}
            \right] &
            \begin{array}{l}
                \left.
                \begin{array}{p{4cm}}
                    right ascension \\
                    declination \\
                    arrival time at geocenter \\
                    inclination angle \\
                    polarization angle \\
                    coalescence phase \\
                    \hdashline[1pt/1pt]
                \end{array}
                \quad \right\} \textnormal{extrinsic} \\
                \left.
                \begin{array}{p{4cm}}
                    first component's mass \\
                    second component's mass \\
                    first component's spin \\
                    second component's spin
                \end{array}
                \quad \right\} \textnormal{intrinsic}
            \end{array}
        \end{array}
\end{equation}

In this work we restrict ourselves to nonspinning sources, where $\mathbf{S}_1=\mathbf{S}_2=0$. Removing nuisance parameters requires either replacing them with their measured values or marginalizing over them. The chirp mass is typically well measured by the detection pipeline, so we use the maximum likelihood value, $\hat{\mathcal{M}}$, for it. We marginalize over the other variables using a uniform prior, i.e.
\begin{equation}
p(\alpha,\delta,D_L|d) = \int\, d\tau_\oplus p_U(\tau_\oplus) d\phi_c p_U(\phi_c) d\phi p_U(\psi)  d\cos(\iota) p_U(\cos(\iota)) p(\alpha,\delta,D_L,\tau_\oplus,\phi_c,\psi,\cos(\iota)|d),
\end{equation}
where $p_U(x)$ denotes a uniform distribution in $x$.
